Modeling effective collector efficiency of sparse and dense arrays of cylindrical collectors in varying states of flow velocity and turbulence

### 2020-07-09 drafts/outline.tex
figured out .tex basics
formatting
nothing major changed
figured out figures
bibliography is working
working on methods section

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Jordan Wingenroth}
\title{Outline}
\begin{document}
TEST
\end{document}

>>>>

% This file should be compiled as such: PdfLatex -> Bibtex -> PdfLatex (x2)

\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{outlines}
\usepackage{xcolor}

\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\small\sffamily}
\linenumbers

\usepackage{graphicx}
\graphicspath{{../pics/}}

\usepackage{natbib}

\author{Jordan Wingenroth, Candace Yee, Justin Nghiem, and Laurel Larsen}

\title{Modeling effective collector efficiency of sparse and dense arrays of cylindrical collectors in varying states of flow velocity and turbulence}

\begin{document}

\maketitle

\paragraph{Editing notes:}

\textcolor{red!75!green}{Parenthetical insertions in this color are author/editor notes referring to the preceding word or phrase}

\paragraph{Figures:}

I'm aiming for 10-12 figures; 3 methods, 7 results or thereabouts:

\begin{itemize}

\item Methods: Direct interception and capture efficiency diagram

\item Methods: Particle size distribution

\begin{figure}[h]
\includegraphics[width=10cm]{wf5-200sizedist.png}
\centering
\caption{Walnut shell particle size distribution}
\end{figure}

\item Methods: Flume floorplan

\end{itemize}

\section{Introduction}

\section{Methods}

\subsection{Theoretical Background}

Suspended particles in flowing water (i.e., waterborne particles) are subject to numerous physicochemical interactions \textcolor{red!75!green}{(better word?)}. Interactions stemming from fluid mechanics include grav

\subsection{Suspended Particle Concentration Model}
\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}

\subsection{Experimental Methods}
\marginpar{Note: Same subsection title as Fauria 2015. Should we change? Any ideas?}

\subsubsection{Materials}

\subsubsection{Particle Concentration Run Protocols}

\subsubsection{Flow Characterization Run Protocols}

\subsection{Statistical Analysis}

\section{Results}

Example citation \citep{Fauria_2015}.

\section{Discussion}

\bibliographystyle{apalike}
\bibliography{refs}

\end{document}
